Viscous Transport in Eroding Porous Media

### 2019-08-27 docs/transport/erosion_transport.tex
correct the minimum distance in transport paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{20 Bodies at a Low Porosity}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We consider a second example with 20 eroding bodies, but with a smaller
initial porosity.  In Figure~\ref{fig:ErodingLow20vort}, we plot the
eroding geometry and porosity at four evenly spaced instances in time.
Again, the color is the vorticity in the bulk whose magnitude is
equivalent to the erosion rate.  Each body is discretized with $N_\iin =
256$, and the smallest distance between two bodies at the initial
condition is $2.16 \times 10^{-2}$.  At this resolution, this
corresponds to a spacing of $3.0814h$ which is too small for the
trapezoid rule to guarantee a sufficiently small quadrature error.  By
applying the Barycentric quadrature rule, there is no issue simulating
the erosion until all the bodies have eroded.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{20 Bodies at a Low Porosity}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We consider a second example with 20 eroding bodies, but with a smaller
initial porosity.  In Figure~\ref{fig:ErodingLow20vort}, we plot the
eroding geometry and porosity at four evenly spaced instances in time.
Again, the color is the vorticity in the bulk whose magnitude is
equivalent to the erosion rate.  Each body is discretized with $N_\iin =
256$, and the smallest distance between two bodies at the initial
condition is $3.29 \times 10^{-4}$.  At this resolution, this
corresponds to a spacing of $0.0471h$ which is too small for the
trapezoid rule to guarantee a sufficiently small quadrature error.  By
applying the Barycentric quadrature rule, there is no issue simulating
the erosion until all the bodies have eroded.
